Incentivizing Exploration with Unbiased Histories

### 2019-04-26 main.tex
Added a ToC.
Proofs in the warmup section: moved the short proof back to the body; the longer proof, made it the last subsection in the section.
warmup: moved the \input statement for the proofs back into the main file.
Moved \input for details of L-level stuff into the right place.
Revised /expanded the abstract.

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{float}
% ======    PACKAGES
\usepackage{slivkins-setup,slivkins-theorems}
%\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
%\usepackage{amsbsy,amscd, bm, bbm}
\usepackage{kpfonts}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[small,bf]{caption}
\setlength{\captionmargin}{30pt}
\usepackage{subcaption}
\captionsetup[sub]{margin=10pt,font=small}
\usepackage{color}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
\usepackage{url}
\usepackage{tocbibind}
\usepackage{enumerate}
\usepackage{mdframed}
\usepackage{comment}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{cleveref}

@@

% a very useful package for edits and comments, from David Kempe (USC)
%\usepackage{color-edits}
%\usepackage[suppress]{color-edits}  % use this to suppress the package
%\addauthor{as}{red}      % as for Alex
%\addauthor{jm}{blue}     % jm for Jieming
%\addauthor{ni}{magenta}     % ni for Nicole
%\addauthor{sw}{brown}     % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.

@@

\author{
Nicole Immorlica \thanks{Microsoft Research, Cambridge, MA. Email: nicimm@microsoft.com.}
\and
Jieming Mao \thanks{University of Pennsylvania, Philadelphia, PA. email: maojm517@gmail.com. Results in this paper were obtained while J. Mao was an intern at Microsoft Research NYC.}
\and
Aleksandrs Slivkins  \thanks{Microsoft Research, New York, NY. email: slivkins@microsoft.com.}
\and
Zhiwei Steven Wu  \thanks{University of Minnesota, Minneapolis, MN. Email: zsw@umn.edu. Results in this paper were obtained while Z.S. Wu was a postdoc at Microsoft Research NYC.}
}
\begin{document}
\begin{titlepage}
\maketitle

\thispagestyle{empty}
\begin{abstract}
In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world. A sequence of agents each chooses an action with the goal of maximizing payoff given estimates of the state of the world.  A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions.  The goal of the algorithm is to minimize the regret of the action sequence.

In this paper, we study a particular class of disclosure policies that use messages, called {\em unbiased subhistories}, consisting of the actions and rewards from by a subsequence of past agents, where the subsequence is chosen ahead of time. One trivial message of this form contains the full history; a disclosure policy that chooses to use such messages risks inducing herding behavior among the agents and thus has regret linear in the number of rounds.  Our main result is a disclosure policy using unbiased subhistories that obtains regret $\tilde{O}(\sqrt{T})$.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
\end{abstract}
\end{titlepage}

@@

\input{2level}

\input{3level}

%l-level in the 10page
\input{llevel-overview}

@@

\appendix
\input{prelim}
\input{app-warmup}
\input{3levelproofs}
\input{llevel}

>>>>

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{mathrsfs}
\usepackage{float}

% ======    PACKAGES
\usepackage{slivkins-setup,slivkins-theorems}
%\usepackage{amsmath, amsfonts, amssymb, amsthm, amsbsy, amscd, bm, bbm}
%\usepackage{amsbsy,amscd, bm, bbm}
\usepackage{nicefrac}
\usepackage{kpfonts}
\usepackage{array}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[small,bf]{caption}
\setlength{\captionmargin}{30pt}
\usepackage{subcaption}
\captionsetup[sub]{margin=10pt,font=small}
\usepackage{color}
\usepackage{ifthen}
\usepackage{xspace}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
%\usepackage[colorlinks,citecolor={black},urlcolor={black},linkcolor={black}]{hyperref}
\usepackage[breaklinks]{hyperref}
\usepackage{url}
\usepackage{tocbibind}
\usepackage{enumerate}
\usepackage{mdframed}
\usepackage{comment}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{cleveref}

@@

% a very useful package for edits and comments, from David Kempe (USC)
\usepackage{color-edits}
%\usepackage[suppress]{color-edits}  % use this to suppress the package
\addauthor{as}{red}      % as for Alex
\addauthor{jm}{blue}     % jm for Jieming
\addauthor{ni}{magenta}     % ni for Nicole
\addauthor{sw}{brown}     % sw for Steven
% e.g. for Alex, provides \asedit{}, \ascomment{} and \asdelete{}.

@@

\date{First version: November 2018\\This version: April 2019}

\author{
Nicole Immorlica \thanks{Microsoft Research, Cambridge, MA. Email: nicimm@microsoft.com.}
\and
Jieming Mao \thanks{University of Pennsylvania, Philadelphia, PA. email: maojm517@gmail.com. Results in this paper were obtained while J. Mao was an intern at Microsoft Research NYC.}
\and
Aleksandrs Slivkins  \thanks{Microsoft Research, New York, NY. email: slivkins@microsoft.com.}
\and
Zhiwei Steven Wu  \thanks{University of Minnesota, Minneapolis, MN. Email: zsw@umn.edu. Results in this paper were obtained while Z.S. Wu was a postdoc at Microsoft Research NYC.}
}

\begin{document}

\maketitle

\begin{abstract}
In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world. A sequence of agents each chooses an action with the goal of maximizing payoff given estimates of the state of the world.  A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions. The goal of the disclosure policy is to minimize the regret of the action sequence \asedit{chosen by the agents. Prior work achieves much progress with disclosure policies that merely recommend an action to each user. However, all this work relies heavily on trust and rationality assumptions, which are standard and yet quite problematic in the context of recommendation systems.}

\asedit{In this paper, we design disclosure policies which incentivize good performance under more plausible behavioral assumptions. Conceptually, we would like to retain the trustworthiness of revealing the full history, while avoiding the herding behavior induced by such disclosure policy (which may lead to regret linear in the time horizon). We focus on messages, called {\em unbiased subhistories}, consisting of the actions and rewards from a subsequence of past agents, where the subsequence is chosen ahead of time. We further require these messages to be \emph{transitive}: if a message includes action and reward from a particular agent, then it also includes the message sent to that agent. We posit a flexible model of agent response, which we argue is plausible for this class of disclosure policies.}

Our main result is a disclosure policy using unbiased, transitive subhistories that obtains regret $\tilde{O}(\sqrt{T})$, where $T$ is the time horizon.  We also exhibit simpler policies with higher, but still sublinear, regret.  These policies can be interpreted as dividing a sublinear number of agents into constant-sized focus groups, whose histories are then fed to future agents.
\end{abstract}

\thispagestyle{empty}
\addtocontents{toc}{\setcounter{tocdepth}{0}}
\newpage
\thispagestyle{empty}
\tableofcontents
\newpage
\addtocontents{toc}{\setcounter{tocdepth}{2}}

@@

\input{2level}
\input{app-warmup}
\input{3level}
\input{3levelproofs}
\input{llevel-overview}
\input{llevel}

@@

\appendix
%\input{prelim}
%\input{app-warmup}
%\input{3levelproofs}
%\input{llevel}
